\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-06-01 doc/sw-system.tex
Crowd analysis

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centerline{
\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}}
\caption{Screenshot of the \sw classification interface.}
\label{fig:screenshot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Understanding crowd, so we can help them learn faster. Understanding
images given the crowd, so we can find lenses.

@@

What are the properties of the crowd? Corner plots: skill, effort, combine to
give contribution. Actual information generated. Making your own luck. How do these depend on
experience (no. of training images). Describe plot features, in stage 1.
Contrast with stage 2. \Fref{fig:crowd:cornerplot}

Who's doing all the work?
Cumulative plot of ``contributions'' (applied skill).
\Fref{fig:crowd:cumulplot}

Information, contribution totals and their interpretation. Inefficiency
measures? Super-users. 
\Tref{tab:crowd:contributions} shows contributions at stage 2 and stage 1

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
\caption{Screenshot of the \sw classification interface.}
\label{fig:screenshot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this section we present our findings about the performance of the  \sw
system, in terms of the information  contributed by the crowd in
\Sref{sec:results:crowd}, and the overall classifications of the training set
that they made.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
\caption{Key properties and contributions of the \sw crowd. Plotted are the
1-D and 2-D marginalized distributions for the logarithms of the 
properties of the agents described in the text. The stage 1 agents are shown
in blue, the stage 2 agents in orange.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We define the following properties of the crowd, as characterised by their
agents, and plot the distributions of their logarithms in
\Fref{fig:crowd:cornerplot}. 
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
volunteer. In stage 1, the mean effort per agent was 259; in the shorter stage
2 it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In stage 1, the mean experience per agent was 29;
in stage 2 (where the training image fequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gain, $\skill$
should  the next subject classified have lens probability 0.5
\Aref{appendix:swap},  in bits. Random classifiers have $\skill = 0.0$,
perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
this increases as training subjects are classified, and the agent's estimates
of its confusion matrix elements improve. In stage 1, the mean skill per agent
was 0.04 bits; in  stage 2 it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
subject classification history, and represents the total  contribution to the
project that volunteer (see the appendix for more discussion of this
quantity). In stage 1, the mean contribution per agent was 34.3 bits; in 
stage 2 it was 33.5.
%
\item{\noindent\bf ``Information:''} The total information $\information$ generated by
the  agent during the volunteer's classification activity. This quantity
depends on the value of each subject's lens probability when that subject was 
presented to the volunteer (\Aref{appendix:swap}), and so there is an element
of luck involved with this quantity: if you never see a high probability
subject, it's hard to generate a large amount of information. You make your
own luck by classifying more subjects.
%
\end{description}

The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
these properties depends on the effort expended by the volunteers. We see that
experience is strongly correlated with effort (as training images are
presented throughout each stage, albeit at decreasing frequency), and that
this is also true for skill. In the second row of \Fref{fig:crowd:cornerplot}
we see that while skills of greater than 0.1 can be attained after just a few
training images, most agents of such low experience have significantly lower
skill. The volunteers in question only classify a few subjects before leaving.
However, at high values of experience and effort, the skill is \emph{always
high}. There seem to be very few agents logging large numbers of
classifications at low skill (although there are one or two exceptions). Most
high effort ``super-users'' have high skill. These two properties are
reflected in both the contributions these volunteers make (third row) and the
information they generate (fourth row).

The distributions for the stage 2 agents (orange) are qualitatively similar to
those for the stage 1 agents (blue). Differences are: 1) the maximum effort
possible at stage 2 is smaller, because fewer subjects were available to be
classifed, but 2) the mean effort expended at stage 2 was higher (perhaps
because the subjects were higher probability, and more compelling); 3) the
information generated per agent was higher at stage 2, because the subjects
had higher probability.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
\caption{Narrow cumulutive distributions of the contributions made by the
agents: for example, 90\% of the stage 2 contributions were made by the
highest contributing  7\% of the crowd. The stage 1 agents are shown in blue,
the stage 2 agents in orange. ``Experienced volunteers'' classified 10 or more
training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
distributions of logarithmic effort, skill, and contribution. To better
quantify the contributions made by the volunteers, we show their cumulative
distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
clearly the importance of the hardest-working, most active volunteers: at
stage 1,  1.0\% of the volunteers -- 374 people -- made 90\% of the
contribution.  At stage 2, where it was not possible to make as
many classifications before running out of subjects, 7.2\% of the volunteers
-- 141 people -- made 90\% of the contribution.

However, it is not the case that only these small groups were capable of
making this large contribution: 9119 volunteers were ``experienced'' in that
they had all classified at least 10 training images; the 374 highest
contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in 
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
\caption{Broad cumulutive distributions of agent skill: 
the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
The stage 1 agents
are shown in blue, the stage 2 agents in orange. ``Experienced volunteers''
classified 10 or more training subjects.}
\label{fig:crowd:cumulskillplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both stage 1 and 2 of the CFHTLS project, with the
total numbers of agents and subjects for comparison. These numbers allow us to
quantify the efficiency of the system.
